Computer Science House Constitution

### 2024-04-07 constitution.tex
added the requested points about chair responsbilities (#162)
Co-authored-by: Ella Soccoli <112343747+esoccoli@users.noreply.github.com>
[Mega PR] Fixed many of the existing issues (#216)
* Started working on mega pr

* First pass of the document

* second pass

* 3rd pass

* Made changes based on reviews from jeremy and ian

* Made changes discussed at meeting yesterday, and also made remaining changes from reviews

* oops i forgor a thing

* oops i forgor a thing v2

* Made requested changes

* made the table 4 columns because I felt like it

* Fixed all the issues :TM:

* non semantic code

% Reference example:
%Test reference \ref{House Objectives} House Objectives.

@@

% ARTICLE I - INTRODUCTION
\article{Introduction}

@@

\asection{Derivation of Authority}
The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Center for Campus Life and the Department of Residence Life.

\asection{House Objectives}
The objectives of Computer Science House are:
\begin{enumerate}
	\item To enhance the education experience of its members
	\item To offer students educational programming with an emphasis in computers
	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community
	\item To provide a friendly and comfortable living environment in the residence halls
\end{enumerate}

\article{Abbreviations and Definitions}
Many of the commonly used abbreviations will be listed here, and the abbreviations will be used throughout the rest of the document.

\begin{enumerate}
	\item Chairperson - Chair
	\item Evaluations - Evals
	\item Research and Development - R\&D
	\item House Improvements - IMPs
	\item Operational Communications - OpComm
	\item House History - History
	\item Public Relations - PR
	\item Socials - Social
	\item Financials - Financial
	\item Executive Board - E-Board
	\item Root Type Person - RTP
	\item Constitutional Maintainer - Maintainer
	\item Introductory - Intro
	\item Department of Residence Life - ResLife
\end{enumerate}

% ARTICLE II - CONSTITUTIONAL STRUCTURE
\article{Constitutional Structure}

\asection{Constitution}
The House Constitution is written and maintained by the House and defines the major aspects, goals, and governing structure of the house.

\asection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the Fall and Spring semesters.
The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.

% ARTICLE IV - MEMBERSHIP
\article{Membership}
There are five major types of membership available to Computer Science House.
Each carries different qualifications, expectations, and privileges.
When describing the different memberships available, the following terms are used:
\begin{description}
	\item[Qualifications:] What qualifications an applicant needs to apply
	\item[Selection:] The process by which an applicant gains membership
	\item[Expectations:] The duties and responsibilities of House members
	\item[Privileges:] The benefits offered to House members
	\item[Evaluations:] The process by which a member is reviewed and assessed
	\item[Leave of Absence:] The process by which a member may leave House for a period of time
	\item[Resignations:] The process by which a member terminates House membership
	\item[Term:] The length of time the membership lasts
\end{description}

@@

\asubsection{Introductory Membership Qualifications}
Intro Membership is open to all RIT students.

\asubsection{Introductory Membership Selection}
Applicants notify the House of their interest in membership by submitting an application to the Evals Director.
They must then undergo the selection process as defined in \ref{Selection Processes}.

\asubsubsection{Selection Processes}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters

% Current RIT students is defined as students who have attended RIT for at least 1 full semester
\asubsubsubsection{Selection Process for Current RIT Students}
\begin{enumerate}
	\item The applicant submits an application to the Evaluations Director for review.
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
	\item The application materials are then reviewed at an Evaluations meeting.
	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the introductory process.
This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member is not required to pay dues during the Introductory Process.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
\asubsubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the introductory process.
This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member is not required to pay dues during the Introductory Process.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

\asubsection{Introductory Membership Expectations}
Intro members are expected to meet all the requirements of the Intro Process, as described in \ref{Expectations of an Introductory Member}.

\asubsection{Introductory Membership Privileges}
Intro members receive the right to use Computer Science House facilities, to attend House functions, and to have housing priority over all persons who are not Computer Science House members.

\asubsection{Introductory Membership Evaluations}
\asubsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\asubsection{The Evaluation Period}
The Process will occur either once or twice per semester, and will last for six (6) weeks.
The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evaluations Director, or by an Executive Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
\asubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to obtain signatures from all Active Members who have passed a Membership Evaluation, all On-Floor Introductory Members, and ten (10) of any combination of the following:
\begin{itemize}
	\item Alumni members
	\item Honorary members
	\item Advisory members
\end{itemize}
At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
\asubsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
\end{itemize}

\asubsubsection{Introductory Evaluation}
The Introductory Evaluation is the process by which House chooses which Introductory Members to extend an offer of Active Membership.
It occurs at the conclusion of the final week of the Process.

\asubsubsubsection{Voting}
On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}.
A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
In order for an Active Member to be counted as a Possible Vote they must meet the requirements outlined in \ref{Expectations of Voting Members}.
Neither absentee nor proxy votes are allowed.
House may choose any of the Outcomes for each member.

\asubsubsubsection{Outcomes}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Introductory Members may be offered Active Membership (\ref{Active Membership}) provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of House.
	\item If an Introductory Member fails to meet the requirements, their membership will be revoked.
	\item An Introductory member may be given a conditional to complete as a means of making up for missing requirements.
		A conditional may be proposed by any member present at the Introductory Evaluation and, if it is approved by the Evaluations Director, is then voted on by House.
		Each conditional consists of a set of additional requirements and a deadline for completing them.
		When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
		A conditional member who does not meet these additional requirements forfeits membership.
\end{enumerate}

\asubsection{Introductory Membership Leave of Absence}
After completion of the Intro Packet, an Intro member may request a leave of absence through the process described in \ref{Leave of Absence}.

\asubsection{Introductory Membership Resignations}
Intro members may resign by submitting the request for termination of membership to the Chair or Evals Director in writing before the completion of the intro process.
\asubsection{Introductory Membership Term}
Intro membership shall last until the end of the Intro Process, at which time active membership is granted or membership is revoked.

@@

\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at RIT who have passed the Intro Evals and their most recent Membership Evals.

\asubsection{Active Membership Selection}

Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director. They will retain their previous Housing Status if applicable.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate.
The Evals Director will then bring them up for an Immediate Relative Majority vote with fifty percent Quorum at the next House meeting.

If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.

\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
Active voting members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.

\asubsubsection{Expectations of House Members}
Active members are required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings and Executive Board candidate speeches, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
\\* \\*
Active members must participate significantly in at least one major project during the academic year.
Members are required to submit a description for this major project to the Executive Board for approval.
As an option to this requirement, members may instead assist on a large number of House activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by the Executive Board.

\asubsection{Active Membership Privileges}
Active Members receive the privilege to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an E-Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with ResLife policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}

\asubsubsection{Expectations of Voting Members}
The following requirements must be met by the beginning of the Introductory Evaluation for an Active Member to be allowed to vote. 
Any of these requirements may be waived by the Evaluations Director or a simple majority vote by the Executive Board
\begin{itemize}
\item Attend all House meetings during the process
\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\end{itemize}
\asubsection{Active Membership Evaluations}
Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.

% ACTIVE MEMBERSHIP EVALUATIONS

\asubsubsection{Evaluations Processes}
During the academic year, a House member is evaluated by the Membership Evaluation.
The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
Semi-Annual Evaluations Meetings are open only to current Active Members.
All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
\\* \\*
At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution used during the respective Evaluation Process.
It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
\asubsubsubsection{Membership Evaluation}
The Membership Evaluation process occurs once per academic year.
It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
The Membership Evaluation shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Evaluation occurs.
A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

\asubsubsubsubsection{Outcomes}
Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
\\* \\*
If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
In either case, the member forfeits their ability to be included on the following year’s roster.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Evaluation.
If the conditional is approved by the Evaluations Director, it is then voted on by House.
Each conditional consists of a set of additional requirements a deadline for completing them.
When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the evaluation.
\asubsubsubsection{Appeals Process}
If a member disagrees with the outcome of any evaluation, (e.g. is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
\\* \\*
If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.

\asubsection{Active Membership Leave of Absence}
An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}

\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chair or Evals Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.

@@

\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evals and departed for reasons other than revocation of House Membership.

\asubsection{Alumni Membership Selection}
Active members who depart house (i.e. resign) after passing the current operating session's Membership Evals are considered to be Alumni in good standing.
\\*\\*
Active members who depart house without passing the current operating session's Membership Evals are considered to be Alumni in bad standing.
This may be appealed to E-Board in order to pursue a different outcome.

@@

\asubsection{Alumni Membership Privileges}
Alumni Members shall receive the right to:
\begin{itemize}
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
\end{itemize}

\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject to any evaluation.

@@

\asection{Honorary and Advisory Memberships}
\asubsection{Honorary Membership Qualifications}
Honorary Membership is open to a person whom the House feels has contributed great personal effort to the House and is deserving of House recognition.
\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the Rochester Institute of Technology professional, academic, or administrative staff.
\asubsection{Honorary and Advisory Membership Selection}
\begin{enumerate}
	\item A House Member submits to the Evals Director a nomination, in writing, for a person they feel is deserving of Honorary or Advisory Membership. The nomination must specify the type of membership the nominee is nominated for.
	\item The Evals Director performs preliminary research on the candidate and presents the findings.
	\item E-Board decides whether or not to present the nomination to the House for a secret ballot House vote.
		If E-Board decides not to present the nomination to the House, the Selection Process ends and the candidate does not become a Member.

>>>>

@@

% ARTICLE I - ABBREVIATIONS
\article{Abbreviations and Definitions}

\subsection{Abbreviations}
% Formatted as abbreviation  full term
\begin{tabular}{ l  l  l l l l}
	Chair   & \textit{Chairperson}            & Maintainer(s) & \textit{Constitutional Maintainer(s)} \\
	CSH     & \textit{Computer Science House} & OpComm        & \textit{Operational Communications}   \\
	E-Board & \textit{Executive Board}        & PR            & \textit{Public Relations}             \\
	Eval(s) & \textit{Evaluation(s)}          & R\&D          & \textit{Research and Development}     \\
	History & \textit{House History}          & ResLife       & \textit{Residence Life}               \\
	IMPs    & \textit{House Improvements}     & RTP(s)        & \textit{Root Type Person(s)}          \\
	Intro   & \textit{Introductory}                                                                   \\
\end{tabular}

\subsection{Definitions}

% Formatted as term | definition
\begin{tabular}{l l}
	Technical Seminar          & \textit{Seminar relating to computing or electronics}                                     \\
	Standard Operating Session & \textit{RIT's fall and spring semesters, excluding institute breaks and final exam weeks} \\
	Total Expenditure          & \textit{funds drawn for a specific event, project, piece of equipment, or service}
\end{tabular}

% ARTICLE II - INTRODUCTION
\article{Introduction}

@@

\asection{Derivation of Authority}
CSH shall recognize that it receives its right to function as a Special Interest House from the Center for Campus Life and the Department of Residence Life.

\asection{House Objectives}
The objectives of CSH are:
\begin{enumerate}
	\item To enhance the education experience of its members
	\item To offer students educational programming with an emphasis in computers
	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community
	\item To provide a friendly and comfortable living environment in the residence halls
\end{enumerate}

% ARTICLE 3 - CONSTITUTIONAL STRUCTURE
\article{Constitutional Structure and Amendment}

\asection{Constitution}
The CSH Constitution is written and maintained by members and defines the major aspects, goals, and governing structure of CSH.
\\*\\
Unless explicitly stated otherwise, the requirements and expectations defined in the Constitution are for the Standard Operating Session.

\subsection{Modifiying the Constitution}
\asubsection{Non-Semantic Changes}
There are two methods for non-semantic change to the Constitution.
A Maintainer may approve any proposed change that does not affect the meaning of the document.
Alternatively, the change may be presented at a House Meeting for discussion followed by an Immediate One-Half Vote with fifty percent quorum.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in during the week.
The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.

% ARTICLE 4 - MEMBERSHIP
\article{Membership}
There are five types of membership available to CSH.
When describing membership types, the following terms are used:
\begin{description}
	\item[Qualifications:] What criteria an applicant needs to be eligible for membership
	\item[Selection:] The process by which an applicant gains membership
	\item[Expectations:] The duties and responsibilities associated with CSH membership
	\item[Privileges:] The benefits offered to members
	\item[Evaluations:] The process by which a member is reviewed and assessed
	\item[Leave of Absence:] The process by which a member may leave CSH during an RIT Leave of Absence
	\item[Resignations:] The process by which a member terminates CSH membership
	\item[Term:] The duration of the membership
\end{description}

@@

\asubsection{Introductory Membership Qualifications}
Intro Membership is open to all students currently enrolled at RIT.

\asubsection{Introductory Membership Selection}
Applicants notify the Evals Director of their interest in membership by submitting an application.
They then undergo the selection process as defined below.

\asubsubsection{Selection Process for Current RIT Students}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item The applicant submits an application to the Evals Director for review.
	\item The applicant participates in an informal interview with three current Active, Alumni, or Honorary Members.
	\item The application materials are reviewed at an Evals meeting.
	      Then an Immediate Relative Majority Vote of attending members is held on whether or not to accept the person as an Intro Member.
\end{enumerate}

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
\asubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During spring semester, the Evals Director selects a group of Active Members to form a Selections Committee.
	      The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by ResLife.
	\item A subset of applicants will be offered Intro Membership and have the opportunity to participate in the Intro Process defined in \ref{The Evaluation Period}.
	      A subset of Intro Members will be offered On-Floor status and will be able to select a room on floor.
	      The other Intro Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}

\asubsection{Introductory Membership Expectations}
Intro Members are expected to meet all the requirements of the Intro Process, as described in \ref{Expectations of an Introductory Member}.
Intro Members are not required to pay membership dues.

\asubsection{Introductory Membership Privileges}
Most membership privileges do not initiate until successful completion of the Intro Process.
This means that until the member has passed the Intro Eval, the member does not have the right to vote on CSH issues and does not count towards quorum.
The member does, however, have the privilege to use CSH's facilities.

\asubsection{Introductory Membership Evaluations}
The Intro Process allows Intro Members to learn about CSH and demonstrate their interest in becoming Active Members. During this period, Intro Members will meet members, learn CSH history, and be evaluated for Active Membership by Active Members.

% fix numbers to be only text
\asubsubsection{The Evaluation Period}
The Intro Process will occur either once or twice per semester, and will last for six weeks.
The process will be initiated by the Evals Director during either the first and second week of each semester. E-Board may approve an extension to the Intro Process by an E-Board Vote.
If an Intro Process is extended, the Intro Eval shall occur at the termination of the extended process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evals Director or by an E-Board Vote, the second Intro Process must begin within nine days of the first process ending.
If a second Intro Process is approved, the Evals Director may initiate a new Intro Packet within the first or second week of the process.

\asubsubsection{The Introductory Packet}
Each Intro Process participant, after the first week, is given two weeks to obtain signatures from all Active Members who have passed a Membership Eval, all On-Floor Intro and Active Members, and ten of any combination of Alumni, Honorary, and Advisory Members.
At the discretion of the Evals Director or as the result of an E-Board Vote, any Intro Packet may be extended to accommodate extenuating circumstances.

\asubsubsection{Expectations of an Introductory Member}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use numbers
Before the end of the Intro Process, an Intro Member is expected to:
\begin{enumerate}
	\item Attend all House Meetings during the Intro Process
	\item Complete the Intro Packet
	\item Attend at least one directorship meeting for each week of the process
	\item Attend at least one CSH social event during the process
	\item Attend at least two Technical Seminars during the process
\end{enumerate}

\asubsubsection{Introductory Evaluation}
The Intro Eval is the process by which Active Members choose which Intro Members to extend an offer of Active Membership.
It occurs at the end of the final week of the Intro Process.

\asubsubsubsection{Voting}
On a member by member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
An Immediate Relative Majority Vote with two-thirds quorum is required for the Eval to be valid.
For an Active Member to be eligible to vote during the Intro Eval they must meet the requirements outlined in \ref{Expectations of Voting Members}.
Neither absentee nor proxy votes are allowed.
Intro Members may be offered any of the outcomes listed in \ref{Outcomes}

\asubsubsubsection{Outcomes}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Intro Members may be offered Active Membership provided they meet the requirements described in \ref{Expectations of an Introductory Member}, at the discretion of attending members.
	\item If an Intro Member fails to meet the requirements, their membership will be revoked.
	\item An Intro Member may be given a conditional to complete as a means of making up for missing requirements.
	      A conditional may be proposed by any member present at the Intro Eval, and if it is approved by the Evals Director, is then voted on by the attending members.
\end{enumerate}

\asubsection{Introductory Membership Leave of Absence}
An Intro Member may request a Leave of Absence through the process described in \ref{Leave of Absence}.

\asubsection{Introductory Membership Resignations}
Intro Members may resign by submitting the request for termination of membership to the Chair or the Evals Director in writing before the completion of the Intro Process.

\asubsection{Introductory Membership Term}
Intro Membership shall last until the end of the Intro Process, at which time Active Membership is granted or membership is revoked.

@@

\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at RIT who have passed the Intro Eval and their most recent Membership Eval.

\asubsection{Active Membership Selection}
Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evals Director. They will retain their previous Housing Status if applicable.
\\*\\*
Any Alumni Member in bad standing, as described in \ref{Alumni Membership Selection}, may become an Active Member by notifying the Evals Director of their intent to participate.
The Evals Director will then bring them up for an Immediate Relative Majority vote with fifty percent quorum at the next House Meeting.
If the vote passes the Alumni is reinstated as an Active Member with Off-Floor Status effective immediately.

\asubsection{Active Membership Expectations}
Active Members are expected to be active participants in CSH as defined in \ref{Expectations of Active Members}.
Active Voting Members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.

\asubsubsection{Expectations of Active Members}
Active Members are required to pay dues as stated in \ref{Collection of Dues}, attend all House Meetings and E-Board candidate speeches, and attend at least fifteen of the directorship meetings for each semester in which they are an Active Member. They are also expected to sign a copy of the Membership Agreement.
\\* \\*
Active Members must participate in at least one major project during the academic year.
Members are required to submit a description for this major project to E-Board for approval.
As an alternative to this requirement, members may instead assist on a large number of CSH activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by E-Board.

\asubsection{Active Membership Privileges}
Active Members receive the privilege to:
\begin{enumerate}
	\item Vote on CSH issues
	\item Hold a position on E-Board
	\item Use CSH facilities
	\item Receive priority for on-floor housing, or apply for On-Floor Status
\end{enumerate}

\asubsubsection{Expectations of Voting Members}
\renewcommand{\theenumi}{\arabic{enumi}} % For this section, we want items to use letters

The following requirements must be met by the beginning of the Intro Eval for an Active Member to be allowed to vote.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend all House Meetings during the Intro Process
	\item Attend at least one directorship meeting for each week of the Intro Process % The number of directorship meetings intended here is equal to the number of the weeks in the process, not just one each week
	\item Attend at least one CSH social event during the Intro Process
	\item Attend at least two Technical Seminars during the Intro Process
\end{enumerate}

\asubsection{Active Membership Evaluations}
Active Members are evaluated annually through the Eval Process as described in \ref{Evaluations Processes}.

% ACTIVE MEMBERSHIP EVALUATIONS
\asubsubsection{Evaluations Processes}
During the academic year, an Active Member is evaluated by the Membership Eval.
The Membership Eval is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
These meetings are open only to Active Members.
All Active Members are expected to attend the these Evals meetings.
\\* \\*
At the beginning of any Eval Process listed herein, the Evals Director must read the sections of the CSH Constitution used during the respective Eval Process.
It is incumbent upon each member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.

\asubsubsubsection{Membership Evaluation}
The Membership Eval occurs once per academic year.
It is performed as part of the Eval Process that takes place during the spring semester to comply with RIT Housing deadlines.

\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of Active Members} at the beginning of the Membership Eval passes their Membership Eval without being voted on.
All Active Members who have not recieved an exemption from E-Board prior to the Membership Eval will be evaluated on a member by member basis by Active Members.
The Membership Eval shall hold members to the objective requirements defined in \ref{Expectations of Active Members} and determine which members may continue as an Active Member in the following academic year.
Exceptions to the requirements may be made, as attending members may choose any of the outcomes for each member, even if the member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Eval occurs.
A Secret Immediate Relative Majority vote with two-thirds quorum is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

\asubsubsubsubsection{Outcomes}
Members who pass the Membership Eval have the option to participate as an Active Member in the following year.
\\* \\*
If a member fails and has never passed a Membership Eval in the past, their membership will be revoked immediately.
If the member fails, but has previously passed a Membership Eval, they will move to Alumni Membership in bad standing, as defined in \ref{Alumni Membership Selection}, at the end of the Standard Operating Session.
In either case, the member forfeits their ability to participate as an Active Member in the following year.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Eval.
If the conditional is approved by the Evals Director, it is then voted on by the attending members as described in \ref{Voting}.
Each conditional consists of a set of additional requirements a deadline for completing them.
Members who are given a conditional have their Eval decision deferred, and therefore maintain their current membership status until the conditional is resolved.
When the deadline expires, the conditional will be brought before E-Board, who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the Eval.

\asubsubsubsection{Appeals Process}
If a member disagrees with the outcome of any Eval and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
\\* \\*
If the member is still unsatisfied after being heard by E-Board, the appeal may be brought to the attention of the ResLife Advisor.

\asubsection{Active Membership Leave of Absence}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters

An Active Member may at any time request a Leave of Absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{enumerate}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{enumerate}

\asubsection{Active Membership Resignations}
An Active Member may resign by submitting, in writing, the reason for resignation to the Chair or the Evals Director.
Instead of forfeiting membership, Active Members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.

@@

\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all former Active Members who passed at least one Membership Eval and departed for reasons other than revocation of membership.

\asubsection{Alumni Membership Selection}
Active Members who resign from CSH after passing the current operating session's Membership Eval are considered to be Alumni in good standing.
\\*\\*
Active Members who depart house without passing the current operating session's Membership Eval are considered to be Alumni in bad standing.
This may be appealed to E-Board in order to pursue a different outcome, as described in \ref{Appeals}.

@@

\asubsection{Alumni Membership Privileges}
Alumni Members have the privilege to use CSH facilities and attend CSH functions.

\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject to any Evals.

@@

\asection{Honorary and Advisory Memberships}

\asubsection{Honorary Membership Qualifications}
Honorary Membership is open to a person whom CSH feels has contributed great personal effort to CSH and is deserving of recognition.

\asubsection{Advisory Membership Qualifications}
Advisory Membership is open to all members of the RIT professional, academic, or administrative staff.

\asubsection{Honorary and Advisory Membership Selection}
\begin{enumerate}
	\item A CSH Member submits a nomination to the Evals Director, in writing, for a person they feel is deserving of Honorary or Advisory Membership. The nomination must specify the type of membership the nominee is nominated for.
	\item The Evals Director performs preliminary research on the candidate and presents the findings.
	\item If E-Board decides not to present the nomination at a House Meeting, the selection process ends and the candidate does not become a member.
	\item If the nomination is presented at a House Meeting for discussion. A Two-Thirds Vote with two-thirds quorum is held to determine whether the nomination is accepted.
	      Ballots are distributed and voting must remain open for a minimum of a forty-eight hour period.
	\item Candidates selected for Honorary Membership are notified of their selection as an Honorary Member and presented with the honor.
	\item Candidates selected for Advisory Membership are notified of their acceptance as CSH Advisors and asked to accept or decline the selection.
\end{enumerate}

\asubsection{Honorary Membership Expectations}
There are no expectations associated with the Honarary Membership status.

\asubsection{Advisory Membership Expectations}
There are no expectations associated with the Advisory Membership status.

\asubsection{Honorary and Advisory Membership Privileges}
Honorary and Advisory Members may advise in CSH issues, use CSH facilities, and attend CSH functions.

\asubsection{Honorary and Advisory Membership Evaluations}
Honorary and Advisory Members are not subject to any Evals.

\asubsection{Honorary and Advisory Membership Resignations}
An Honorary or Advisory Member may resign by submitting in writing the reason for resignation to the Chair.
The resignation will be read at the following House Meeting and become effective at that time.

\asubsection{Honorary and Advisory Membership Term}
Honorary and Advisory Memberships shall last until the member resigns.

\asection{Leave of Absence}
A Leave of Absence offers the option for members to take extended time away from their responsibilities to CSH for any number of personal issues including, but not limited to, physical illness, mental illness, or caregiving for a sick family member.
In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence, located at \url{https://www.rit.edu/policies/d021}. Additionally, the member should notify the Evals Director of their Leave, at which point they become exempt from all CSH requirements until they return.

% ARTICLE V - OFFICERS OF THE HOUSE
\article{Computer Science House Officers}
